### 2017-05-08 MSSM/MSSM.tex
First part of first round of corrections

\chapter{\texorpdfstring{Search for MSSM \AHtotautau}{Search for MSSM A/H -->tautau}}
\label{chap:mssm}
In this chapter the search for neutral Higgs bosons \PHiggs or \PHiggsps
decaying to a pair of tau leptons is discussed. The results presented
here correspond to those from an analysis performed on a dataset collected
during the first half of the 2016 p-p running period of the \ac{LHC} \cite{CMS-PAS-HIG-16-037}. %This dataset
%corresponds to an integrated luminosity of $12.9\,\invfb$, and the analysis is
%detailed in reference \cite{CMS-PAS-HIG-16-037}. 
The \etau, \mutau, \tautau and \emu final
states of the di-tau pair were studied. The results of this search are 
model-independent upper limits on \xsbr of \PHiggs or \PHiggsps 
production in the gluon fusion ($\Pgluon\Pgluon\phi$) and b-associated ($\Pbottom\Pbottom\phi$) production 
modes (see chapter \ref{chap:theory}) and decay into $\Pgt\Pgt$. 
In addition to the upper limits on \xsbr of these two processes, 
the results are interpreted in \ac{MSSM} benchmark scenarios.
A very similar analysis, not described in detail here,
was performed on a dataset corresponding to $2.3\,\invfb$ collected at $\sqrt{s}=13\,\TeV$ during the 2015 \ac{LHC} p-p running period.  
More information can be found in reference \cite{CMS-PAS-HIG-16-006}.

@@

The basis of the event selection is to identify \mutau, \etau,
\tautau and \emu pairs. Events are selected first by using a trigger,
followed by additional selection criteria. For the \etau
and \mutau channels events are selected by only triggering on the electron or muon. 
While the lepton + hadronic tau cross-triggers that are also available
allow for a $3\,\GeV$ ($6\,\GeV$) lower \pT~threshold on the
muon (electron), the benefit of using such a trigger is small: 
most of the signals at high mass, the region of interest in this
analysis, have higher \pT~electrons and muons. This is illustrated
in figure \ref{fig:mt_muonpt}a, which shows the \pT~of muons in the
\mutau channel. The signal is overlaid, with a normalisation of 4000 times its \xsbr 
 at \mA~$=1\,\TeV$ and \tanb~$=50$ in the $m_{\PHiggslight}^{\text{mod}+}$ scenario.
In the \emu channel two dedicated electron-muon cross-triggers
are used. These have significantly lower \pT~cuts 
on the two leptons than the single lepton triggers. For the 
\tautau channel a di-tau trigger is used.

@@

\subsection{Pair selection and vetoes}
\label{sec:mssm_eventsel_pairs}
After applying trigger
requirements, identification criteria and kinematic cuts
more than one possible candidate pair can exist. If
this is the case the pair with the two most isolated candidates
 is chosen, as isolated candidates are less likely 
to be jets mis-reconstructed
as leptons or hadronic taus.
%If this
%is the case for an event, the pair is chosen as follows:
%\begin{itemize}
%\setlength{\itemsep}{-\baselineskip}
%\item Prefer the pair with most isolated candidate 1 (muon for \mutau and \emu channels,
%electron for \etau channel, either of the $\Pgt_h$s in \tautau channel). For electrons
%and muons this means the object with the smallest relative isolation value is preferred, for $\Pgt_h$s the
%object with raw MVA isolation value nearest to 1.
%\item If the isolation of candidate 1 is the same in both pairs, prefer the pair with highest candidate 1 \pT.
%\item If the \pT~of candidate 1 is the same in both pairs, prefer the pair with most isolated
%candidate 2 (e for the \emu channel, the other $\Pgt_h$ for the \tautau channel, 
%and the $\Pgt_h$ for \etau and \mutau channels).
%\item If the isolation of candidate 2 is the same in both pairs, prefer the pair with highest candidate 2 \pT.
%\end{itemize}

@@

The isolation variables studied include
the $\Delta\beta$ corrected isolation variable analogous
to the one given for electrons in equation \ref{eqn:electron_reliso} with 
isolation cone sizes of 0.3 and 0.4 in $\Delta R$. In addition
to this a very similar
variable, which does not just consider charged \ac{PF} hadrons but
also electrons and muons in the isolation sum, is considered. This
variable is also studied for cone sizes of 0.3 and 0.4. Finally,
a relative isolation variable based solely on the \pT~of tracks from the primary
vertex,
\begin{equation}\label{eqn:reltrkiso}
I_{\text{trk}} = \frac{\Sigma p_{\text{T}}^{\text{tracks from PV within cone of 0.3 of the muon}}}{p_{\text{T}}^{\mu}}, \end{equation} 
is studied. The $S/\sqrt{B}$ for the different isolation variables is shown in figure \ref{fig:mssm_selection_mt_muons}a, with the
size of the error interval from the maximum-likelihood fit to the \Ztautau signal strength shown in 
\ref{fig:mssm_selection_mt_muons}b. Both figures of merit do not
change significantly when varying the isolation requirements meaning that this analysis
is not so sensitive to fake, non-isolated muons. The choice of isolation variable is therefore
driven mostly by simplicity and consistency with other \ac{CMS} analyses.

@@

In addition to the selection described so far,
 a topological selection is made on the $D_{\zeta}$ variable \cite{cdf-dzeta},
\begin{align}\label{eqn:mssm_em_dzeta}
D_{\zeta} = P_{\zeta} - 1.85 P_{\zeta}^{\text{vis}}, \notag \\
\text{where } P_{\zeta} = (\vec{p}_{\text{T},1}^{\text{  vis}} + \vec{p}_{\text{T},2}^{\text{  vis}} + E_{\text{T}}^{\text{miss}})\frac{\vec{\zeta}}{|\vec{\zeta}|} 
\text{ and } P_{\zeta}^{\text{vis}} = (\vec{p}_{\text{T},1}^{\text{  vis}}+\vec{p}_{\text{T},2}^{\text{  vis}})\frac{\vec{\zeta}}{|\vec{\zeta}|}.
\end{align}
This means $D_{\zeta}$ is defined as the projection of the transverse momenta of the visible tau decay products plus missing energy, \pT+\MET, onto 
the axis $\vec{\zeta}$, minus the projection of only the transverse momenta of the visible tau decay products onto this axis.
The axis $\vec{\zeta}$ is the axis that bisects
the directions $\vec{p}_{\text{T,1}}^{\text{  vis}}$ and $\vec{p}_{\text{T,2}}^{\text{  vis}}$
of the visible decay products in the transverse plane. This definition is illustrated in figure
\ref{fig:mssm_dzeta}a, with figure \ref{fig:mssm_dzeta}b showing the $D_{\zeta}$ distribution
for \emu events. The selection used, $D_{\zeta} > -20\,\GeV$, rejects $\ttbar$, \Wjets and di-boson
events. 
%The momentum of the neutrinos should not be in the opposite direction of the sum of the visible decay products
%as the neutrinos and visible tau decay products travel at small angles from the original tau.

@@

\section{\acl{MC} simulation to data correction factors}

@@

data are used to derive the \ac{MC} simulation to data correction factors

@@

The \Wjets process is a background in the \etau and \mutau channels when the lepton from the \PW boson decay and a jet mis-reconstructed
as a hadronic tau form a pair. In the \tautau channel it is a background when one \Pgth originates from a $\PW \rightarrow \Pgt\Pgn$ decay
and the other from an additional jet in the event being mis-reconstruced as a hadronic tau. 
In the \emu channel an additional lepton would have to originate from one of the jets, and so in this
channel this background is smaller. The di-boson and single-top backgrounds are small in all channels. In
figures the di-boson and single-top backgrounds are drawn together with the \Wjets 
background and labelled collectively as the `Electroweak' component.

@@

The method described so far works well in the no b-tag categories, but in the b-tag category of both channels
the \ttbar background dominates. This is illustrated in figure \ref{fig:bkgs_highmtctrl}, where
the high-\mT~region in the no b-tag category, figure \ref{fig:bkgs_highmtctrl}a, is compared with the high-\mT~region in the 
b-tag category, figure \ref{fig:bkgs_highmtctrl}b, of the \etau channel. It is clear that the \ttbar 
background is much larger than the \Wjets background in the b-tag high-\mT~control region.
For this reason the estimate of the number
of \Wjets events in this category is made with a relaxed category selection where the b-tagging
requirement itself is removed, but the jet requirements remain. Events with at least one 
jet with $\pTm>20\,\GeV$ and with $|\eta|<2.4$, but at most one jet with $\pTm>30\,\GeV$ and $|\eta|<4.7$, are therefore selected. The final \Wjets estimate in the b-tag category signal
region is determined by the estimate given by the number of \Wjets events
estimated in this one-jet selection, multiplied by an extrapolation factor 
$\frac{N_{\text{W,MC}}^{\text{OS,low } m_{\text{T}},\text{b-tag category}}}{N_{\text{W,MC}}^{\text{OS, low }m_{\text{T}},\text{one-jet selection}}}$.
\begin{figure}[h!]
\begin{center}
\subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_et_10_shapes_postfit.pdf}}
\subfloat[B-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_et_13_shapes_postfit.pdf}}
\end{center}
\caption[High-\mT~control region in the no b-tag and b-tag
categories of the \etau channel.]{High-\mT~control region in the (a) no b-tag and (b) b-tag categories of the \etau
channel. In the no b-tag category the \Wjets background, drawn together with the small
 di-boson plus single-top backgrounds as the `electroweak' background component, dominates. In the b-tag
category the \ttbar background is larger than the \Wjets background.}
\label{fig:bkgs_highmtctrl}
\end{figure}

@@

\subsubsection{\texorpdfstring{\tautau channel}{tau tau channel}}
\label{sec:mssm_bkgs_qcd_tt}
In the \tautau channel QCD events constitute by far the dominant background.
The normalisation and shape 
of this background are estimated from a sideband with relaxed 
isolation requirements with respect to the signal region. 
In the no b-tag category the sideband used is defined
by having the \Pgth with highest \pT~pass the tight working
point of the tau isolation discriminator, as in the nominal selection.
The other \Pgth is required to fail the tight working point,
but pass the medium working point. This sideband is 
chosen as it is as close to the signal region as possible, and 
this should minimise biases in the shape of the total transverse mass
distribution. Other backgrounds
in this sideband are subtracted from the observation to give
the QCD estimate. Differences in normalisation due to
the use of a loosened sideband are corrected for by the medium-to-tight isolation
scale factor. This correction factor is measured as
\begin{equation}\label{eqn:tautau_qcd}
R_{\text{QCD}}^{\text{medium}\rightarrow\text{tight}} = \frac{N_{\text{data}}^{SS,\text{nominal isolation}}-N_{\text{other bkgs}}^{SS,\text{loosened isolation}}}{N_{\text{data}}^{SS,\text{loosened isolation}}-N_{\text{other bkgs}}^{SS,\text{loosened isolation}}}.
\end{equation}
This correction factor takes the ratio between the background-subtracted data in regions 
equivalent to the signal region and the sideband with relaxed isolation, but with the
charge requirement on the pair inverted.

@@

\section{Systematic uncertainties}
\label{sec:mssm_uncs}
As for the analysis presented in chapter \ref{chap:hhh}
two types of systematic uncertainty are considered. Normalisation
uncertainties only affect the yield of a process while shape
uncertainties affect both the process normalisation and the shape
of the \mTtot~distribution. The uncertainties are taken into account 
in the final result as described in section \ref{sec:hhh_results_extraction}.

@@

\subsection{MSSMvsSM hypothesis testing}
\label{sec:mssm_sigext_mssmvssm}
The results of the search are interpreted in \ac{MSSM} benchmark
scenarios, with the interpretation made in the \mA-\tanb~plane.
At each point in the \mA-\tanb~plane each \ac{MSSM} scenario
predicts a production cross section, and a corresponding branching
ratio into $\Pgt\Pgt$, for each of the three neutral Higgs bosons. The
masses of the light \PHiggslight and the scalar \PHiggs are also given as a function of \mA~and \tanb.
To interpret the results of this search in a particular scenario, the predicted
signal from the three neutral Higgs bosons is combined into a single signal template\footnote{Examples of what such a combined signal profile might look like are given in figures \ref{fig:mssm_results_mttot_mt}--\ref{fig:mssm_results_mttot_em},
which give the \mTtot~distributions for all channels and categories with an example three-Higgs boson signal overlaid.}.
In this way the compatibility of the data with all three Higgs bosons, not just a single one, is tested.

@@

The modification of the likelihood function means it is no longer possible
to use the profile likelihood ratio of equation \ref{eqn:hhh_profilelikelihood}:
a test of $\mu=1$ against $\mu=0$ has to be made, and 
$\hat{\mu}$ in the denominator of equation \ref{eqn:hhh_profilelikelihood} is in 
general not zero. A solution to this problem can be found in the test statistic used at the Tevatron \cite{LHCHComb2011},
\begin{equation}\label{eqn:mssm_tevatron_teststat}
q_{\mu} = -2\text{ln }\frac{\mathcal{L}(\text{data}|\mu,\hat{\theta_{\mu}})}{\mathcal{L}(\text{data}|0,\hat{\theta_0})} \text{ with } 0\leq\mu.
\end{equation}
In this test statistic a positive value of $\mu$ is tested against $\mu=0$, thus 
the desired `MSSMvsSM' test statistic can be defined, using $\mu=1$, as,
\begin{equation}\label{eqn:mssm_mssmvssm_stat}
q_{\text{MSSMvsSM}} = -2\text{ln }\frac{\mathcal{L}(\text{data}|s_{\text{MSSM}}(\theta) + b(\theta))}{\mathcal{L}(\text{data}|s_{\text{SM}}(\theta)+b(\theta))}.
\end{equation}

The asymptotic approximation, discussed in section \ref{sec:hhh_results_extraction}, can not be applied
to this test statistic, and therefore the probability density functions need to be generated 
with toy datasets. Using these probability density functions $\text{CL}_s(\mu=1)$ can be calculated as defined in equation \ref{eqn:hhh_cls}.
If $\text{CL}_s < 0.05$ the \ac{MSSM} hypothesis is excluded at the 95\% CL. The generation of toy datasets and 
calculation of corresponding $\text{CL}_s$ values is performed for many points in a grid in the \mA-\tanb~plane,
with interpolation between grid points performed to obtain a smooth exclusion contour.
The probability distribution functions for the \ac{SM} and \ac{MSSM} hypotheses, as well as the resulting $\text{CL}_s$ values,
are given for three illustrative \mA-\tanb~points in figure \ref{fig:mssm_mssmvssm_toys}. In figure \ref{fig:mssm_mssmvssm_toys}a
there is no separation between the \ac{MSSM} and \ac{SM} distributions, and so this point cannot be excluded. The separation
between the distributions in figure \ref{fig:mssm_mssmvssm_toys}b is much improved, and the observation is most compatible
with the \ac{SM} hypothesis. This point is on the edge of being excluded. Finally the distributions in figure \ref{fig:mssm_mssmvssm_toys}c
are very well separated, and the observation is compatible with the \ac{SM} hypothesis, meaning this point of the parameter space is excluded.

>>>>

\chapter{\texorpdfstring{Search for MSSM \AHtotautau}{Search for MSSM A/H -->tautau}}
\label{chap:mssm}
In this chapter the search for neutral Higgs bosons \PHiggs or \PHiggsps
decaying to a pair of tau leptons is discussed. The results presented
here correspond to those from an analysis performed on a dataset collected
during the first half of the 2016 p-p running period of the \ac{LHC} \cite{CMS-PAS-HIG-16-037}. %This dataset
%corresponds to an integrated luminosity of $12.9\,\invfb$, and the analysis is
%detailed in reference \cite{CMS-PAS-HIG-16-037}. 
The \etau, \mutau, \tautau and \emu final
states of the di-tau pair were studied. The results of this search are 
model-independent upper limits on \xsbr of \PHiggs or \PHiggsps 
production in the gluon fusion ($\Pgluon\Pgluon\phi$) and b-associated ($\Pbottom\Pbottom\phi$) production 
modes and decay into $\Pgt\Pgt$. 
In addition to the upper limits on \xsbr of these two processes, 
the results are interpreted in \ac{MSSM} benchmark scenarios.
A very similar analysis, not described in detail here,
was performed on a dataset corresponding to $2.3\,\invfb$ collected at $\sqrt{s}=13\,\TeV$ during the 2015 \ac{LHC} p-p running period.  
More information can be found in reference \cite{CMS-PAS-HIG-16-006}.

@@

The basis of the event selection is to identify \mutau, \etau,
\tautau and \emu pairs. Events are selected first by using a trigger,
followed by additional selection criteria. For the \etau
and \mutau channels, events are selected by only triggering on the electron or muon. 
While the lepton + hadronic tau cross-triggers that are also available
allow for a $3\,\GeV$ ($6\,\GeV$) lower \pT~threshold on the
muon (electron), the benefit of using such a trigger is small: 
most of the signals at high mass, the region of interest in this
analysis, have higher \pT~electrons and muons. This is illustrated
in figure \ref{fig:mt_muonpt}a, which shows the \pT~of muons in the
\mutau channel. The signal is overlaid, with a normalisation of 4000 times its \xsbr 
 at \mA~$=1\,\TeV$ and \tanb~$=50$ in the $m_{\PHiggslight}^{\text{mod}+}$ scenario.
In the \emu channel two dedicated electron-muon cross-triggers
are used. These have significantly lower \pT~cuts 
on the two leptons than the single lepton triggers. For the 
\tautau channel a di-tau trigger is used.

@@

\subsection{Pair selection and vetoes}
\label{sec:mssm_eventsel_pairs}
After applying trigger
requirements, identification criteria and kinematic cuts,
more than one possible candidate pair can exist. If
this is the case the pair with the two most isolated candidates
 is chosen, as isolated candidates are less likely 
to be jets mis-reconstructed
as leptons or hadronic taus.
%If this
%is the case for an event, the pair is chosen as follows:
%\begin{itemize}
%\setlength{\itemsep}{-\baselineskip}
%\item Prefer the pair with most isolated candidate 1 (muon for \mutau and \emu channels,
%electron for \etau channel, either of the $\Pgt_h$s in \tautau channel). For electrons
%and muons this means the object with the smallest relative isolation value is preferred, for $\Pgt_h$s the
%object with raw MVA isolation value nearest to 1.
%\item If the isolation of candidate 1 is the same in both pairs, prefer the pair with highest candidate 1 \pT.
%\item If the \pT~of candidate 1 is the same in both pairs, prefer the pair with most isolated
%candidate 2 (e for the \emu channel, the other $\Pgt_h$ for the \tautau channel, 
%and the $\Pgt_h$ for \etau and \mutau channels).
%\item If the isolation of candidate 2 is the same in both pairs, prefer the pair with highest candidate 2 \pT.
%\end{itemize}

@@

The isolation variables studied include
the $\Delta\beta$ corrected isolation variable analogous
to the one given for electrons in equation \ref{eqn:electron_reliso} with 
isolation cone sizes of 0.3 and 0.4 in $\Delta R$. In addition
to this a very similar
variable, which does not just consider charged \ac{PF} hadrons but
also electrons and muons in the isolation sum, is considered. This
variable is also studied for cone sizes of 0.3 and 0.4. Finally,
a relative isolation variable based solely on the \pT~of tracks from the primary
vertex,
\begin{equation}\label{eqn:reltrkiso}
I_{\text{trk}} = \frac{\Sigma p_{\text{T}}^{\text{trkPV}}}{p_{\text{T}}^{\mu}}, \end{equation} 
where `trkPV' refers to tracks from the primary vertex which are within a cone of $\Delta R=0.3$ of the muon,
is studied. The $S/\sqrt{B}$ for the different isolation variables is shown in figure \ref{fig:mssm_selection_mt_muons}a, with the
size of the error interval from the maximum-likelihood fit to the \Ztautau signal strength shown in 
\ref{fig:mssm_selection_mt_muons}b. Both figures of merit do not
change significantly when varying the isolation requirements meaning that this analysis
is not so sensitive to fake, non-isolated muons. The choice of isolation variable is therefore
driven mostly by simplicity and consistency with other \ac{CMS} analyses.

@@

In addition to the selection described so far,
 a topological selection is made on the $D_{\zeta}$ variable \cite{cdf-dzeta},
\begin{align}\label{eqn:mssm_em_dzeta}
&D_{\zeta} = P_{\zeta} - 1.85 P_{\zeta}^{\text{vis}}, \notag \\
&\text{where } P_{\zeta} = (\vec{p}_{\text{T},1}^{\text{  vis}} + \vec{p}_{\text{T},2}^{\text{  vis}} + E_{\text{T}}^{\text{miss}})\frac{\vec{\zeta}}{|\vec{\zeta}|} 
\text{ and } P_{\zeta}^{\text{vis}} = (\vec{p}_{\text{T},1}^{\text{  vis}}+\vec{p}_{\text{T},2}^{\text{  vis}})\frac{\vec{\zeta}}{|\vec{\zeta}|}.
\end{align}
This means $D_{\zeta}$ is defined as the projection of the transverse momenta of the visible tau decay products plus missing energy, \pT+\MET, onto 
the axis $\vec{\zeta}$, minus the projection of only the transverse momenta of the visible tau decay products onto this axis.
The axis $\vec{\zeta}$ is the axis that bisects
the directions $\vec{p}_{\text{T,1}}^{\text{  vis}}$ and $\vec{p}_{\text{T,2}}^{\text{  vis}}$
of the visible decay products in the transverse plane. This definition is illustrated in figure
\ref{fig:mssm_dzeta}a, with figure \ref{fig:mssm_dzeta}b showing the $D_{\zeta}$ distribution
for \emu events. The selection used, $D_{\zeta} > -20\,\GeV$, rejects $\ttbar$, \Wjets and di-boson
events. 
%The momentum of the neutrinos should not be in the opposite direction of the sum of the visible decay products
%as the neutrinos and visible tau decay products travel at small angles from the original tau.

@@

\section{\acl{MC} simulation-to-data correction factors}

@@

data are used to derive the \ac{MC} simulation-to-data correction factors

@@

The \Wjets process is a background in the \etau and \mutau channels when the lepton from the \PW boson decay and a jet mis-reconstructed
as a hadronic tau form a pair. In the \tautau channel it is a background when one \Pgth originates from a $\PW \rightarrow \Pgt\Pgn$ decay
and the other from an additional jet in the event being mis-reconstruced as a hadronic tau. 
In the \emu channel an additional lepton would have to originate from one of the jets, and so in this
channel this background is smaller. The di-boson and single-top backgrounds are small in all channels. In all
figures in this chapter the di-boson and single-top backgrounds are drawn together with the \Wjets 
background and labelled collectively as the `Electroweak' component.

@@

The method described so far works well in the no b-tag categories, but in the b-tag category of both channels
the \ttbar background dominates. This is illustrated in figure \ref{fig:bkgs_highmtctrl}, where
the high-\mT~region in the no b-tag category, figure \ref{fig:bkgs_highmtctrl}a, is compared with the high-\mT~region in the 
b-tag category, figure \ref{fig:bkgs_highmtctrl}b, of the \etau channel. It is clear that the \ttbar 
background is much larger than the \Wjets background in the b-tag high-\mT~control region.
For this reason the estimate of the number
of \Wjets events in this category is made with a relaxed category selection where the b-tagging
requirement itself is removed, but the jet requirements remain. Events with at least one 
jet with $\pTm>20\,\GeV$ and with $|\eta|<2.4$, but at most one jet with $\pTm>30\,\GeV$ and $|\eta|<4.7$, are therefore selected. The final \Wjets estimate in the b-tag category signal
region is determined by the estimate given by the number of \Wjets events
estimated in this one-jet selection, multiplied by an extrapolation factor 
$N_{\text{W,MC}}^{\text{OS,low } m_{\text{T}},\text{b-tag category}}/N_{\text{W,MC}}^{\text{OS, low }m_{\text{T}},\text{one-jet selection}}$.
\begin{figure}[h!]
\begin{center}
\subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_et_10_shapes_postfit.pdf}}
\subfloat[B-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_et_13_shapes_postfit.pdf}}
\end{center}
\caption[High-\mT~control region in the no b-tag and b-tag
categories of the \etau channel.]{High-\mT~control region in the (a) no b-tag and (b) b-tag categories of the \etau
channel. In the no b-tag category the \Wjets background, drawn together with the small
 di-boson plus single-top backgrounds as the `electroweak' background component, dominates. In the b-tag
category the \ttbar background is larger than the \Wjets background.}
\label{fig:bkgs_highmtctrl}
\end{figure}

@@

\subsubsection{\texorpdfstring{\tautau channel}{tau tau channel}}
\label{sec:mssm_bkgs_qcd_tt}
In the \tautau channel QCD events constitute by far the dominant background.
The normalisation and shape 
of this background are estimated from a sideband with relaxed 
isolation requirements with respect to the signal region. 
In the no b-tag category the sideband used is defined
by having the \Pgth with highest \pT~pass the tight working
point of the tau isolation discriminator, as in the nominal selection.
The other \Pgth is required to fail the tight working point,
but pass the medium working point. This sideband is 
chosen as it is as close to the signal region as possible, and 
this should minimise biases in the shape of the total transverse mass
distribution. Other backgrounds
in this sideband are subtracted from the observation to give
the QCD estimate. Differences in normalisation due to
the use of a loosened sideband are corrected for by the medium-to-tight isolation
scale factor. This correction factor is measured as
\begin{equation}\label{eqn:tautau_qcd}
R_{\text{QCD}}^{\text{medium}\rightarrow\text{tight}} = \frac{N_{\text{data}}^{SS,\text{nominal isolation}}-N_{\text{other bkgs}}^{SS,\text{nominal isolation}}}{N_{\text{data}}^{SS,\text{loosened isolation}}-N_{\text{other bkgs}}^{SS,\text{loosened isolation}}}.
\end{equation}
This correction factor takes the ratio between the background-subtracted data in regions 
equivalent to the signal region and the sideband with relaxed isolation, but with the
charge requirement on the pair inverted.

@@

\section{Systematic uncertainties}
\label{sec:mssm_uncs}
As for the \Htohhtobbtautau analysis
two types of systematic uncertainty are considered. Normalisation
uncertainties only affect the yield of a process while shape
uncertainties affect both the process normalisation and the shape
of the \mTtot~distribution. The uncertainties are taken into account 
in the final result as described in section \ref{sec:hhh_results_extraction}.

@@

\subsection{MSSM vs SM hypothesis testing}
\label{sec:mssm_sigext_mssmvssm}
The results of the search are interpreted in \ac{MSSM} benchmark
scenarios, with the interpretation made in the \mA-\tanb~plane.
At each point in the \mA-\tanb~plane each \ac{MSSM} scenario
predicts a production cross section, and a corresponding branching
ratio into $\Pgt\Pgt$, for each of the three neutral Higgs bosons. The
masses of the light \PHiggslight and the scalar \PHiggs are also given as a function of \mA~and \tanb.
To interpret the results of this search in a particular scenario, the predicted
signal from the three neutral Higgs bosons is combined into a single signal template\footnote{Examples of what such a combined signal profile might look like are given in figures \ref{fig:mssm_results_mttot_mt}--\ref{fig:mssm_results_mttot_em},
which give the \mTtot~distributions for all channels and categories with an example three-Higgs boson signal overlaid.}.
In this way the compatibility of the data with all three Higgs bosons, not just a single one, is tested.

@@

The modification of the likelihood function means it is no longer possible
to use the profile likelihood ratio of equation \ref{eqn:hhh_profilelikelihood}:
a test of $\mu=1$ against $\mu=0$ has to be made, and 
$\hat{\mu}$ in the denominator of equation \ref{eqn:hhh_profilelikelihood} is in 
general not zero. A solution to this problem can be found in the test statistic used at the Tevatron \cite{LHCHComb2011,TEV-Higgs},
\begin{equation}\label{eqn:mssm_tevatron_teststat}
q_{\mu} = -2\text{ln }\frac{\mathcal{L}(\text{data}|\mu,\hat{\theta_{\mu}})}{\mathcal{L}(\text{data}|0,\hat{\theta_0})} \text{ with } 0\leq\mu.
\end{equation}
In this test statistic a positive value of $\mu$ is tested against $\mu=0$, thus 
the desired `MSSMvsSM' test statistic can be defined, using $\mu=1$, as,
\begin{equation}\label{eqn:mssm_mssmvssm_stat}
q_{\text{MSSMvsSM}} = -2\text{ln }\frac{\mathcal{L}(\text{data}|s_{\text{MSSM}}(\theta) + b(\theta))}{\mathcal{L}(\text{data}|s_{\text{SM}}(\theta)+b(\theta))}.
\end{equation}

The asymptotic approximation, discussed in section \ref{sec:hhh_results_extraction}, cannot be applied
to this test statistic, and therefore the probability density functions need to be generated 
with toy datasets. Using these probability density functions, $\text{CL}_s(\mu=1)$ can be calculated as defined in equation \ref{eqn:hhh_cls}.
If $\text{CL}_s < 0.05$, the \ac{MSSM} hypothesis is excluded at the 95\% CL. The generation of toy datasets and 
calculation of corresponding $\text{CL}_s$ values is performed for many points in a grid in the \mA-\tanb~plane,
with interpolation between grid points performed to obtain a smooth exclusion contour.
The probability distribution functions for the \ac{SM} and \ac{MSSM} hypotheses, as well as the resulting $\text{CL}_s$ values,
are given for three illustrative \mA-\tanb~points in figure \ref{fig:mssm_mssmvssm_toys}. In figure \ref{fig:mssm_mssmvssm_toys}a
there is no separation between the \ac{MSSM} and \ac{SM} distributions, and so this point cannot be excluded. The separation
between the distributions in figure \ref{fig:mssm_mssmvssm_toys}b is much improved, and the observation is most compatible
with the \ac{SM} hypothesis. This point is on the edge of being excluded. Finally the distributions in figure \ref{fig:mssm_mssmvssm_toys}c
are very well separated, and the observation is compatible with the \ac{SM} hypothesis, meaning this point of the parameter space is excluded.
